Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
add caption for fig3
fix typo caption fig1

\subsection{Learning Schemes}
\begin{figure}
  \centering
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-ctde.pdf}
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
  \caption{Graphical rap presentation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
  \label{fig:learning_paradigms}
\end{figure}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{TODO
  }
  \label{fig:behavior}
\end{figure}

>>>>

\subsection{Learning Schemes}
\begin{figure}
  \centering
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-ctde.pdf}
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
  \caption{Graphical representation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
  \label{fig:learning_paradigms}
\end{figure}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{Graphical representation of wanted and unwanted behaviors.
  On the left, the wanted behavior, the agents correctly cooperate to cover
  two different items.
  While, on the right, the agents do not correctly cooperate covering
  the same item.
  }
  \label{fig:behavior}
\end{figure}
